---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# CAST_Shiny 0.0.2.9011 (2025-12-04)

* refactor: Remove comparator info from Set Up Tool tab
* refactor: Update explore watershed stressor radio button based on metadata

# CAST_Shiny 0.0.2.9010 (2025-12-04)

* refactor: Update set up select target site to not auto select the firs site
* refactor: Add shiny alert for no site selected for run report
* refactor: Include any extra user files in RDS check files download zip file

# CAST_Shiny 0.0.2.9009 (2025-12-04)

* refactor: Update check files uploaded files check boxes based on files present in user files

# CAST_Shiny 0.0.2.9008 (2025-12-04)

* refactor: Add variable for check files qc tables row colors to global
* refactor: Add bold font for false results to check files qc tables
* refactor: Trigger to stop process when check files if any missing
    + Add Shiny alert

# CAST_Shiny 0.0.2.9007 (2025-12-02)

* fix: Update check files qc table displays

# CAST_Shiny 0.0.2.9006 (2025-12-02)

* refactor: Updates for run report
* refactor: Change directory structure for check files and run report
* fix: Download buttons for check files
* refactor: Update check files zip to include RDS and check tables
    + Tables needed for run report

# CAST_Shiny 0.0.2.9005 (2025-11-13)

* refactor: Update clean_dir helper function
    + Option for include directories
* style: Add roxygen styling to clean_dir function

# CAST_Shiny 0.0.2.9004 (2025-10-10)

* refactor: Add check files to Shiny
* refactor: Update server code for check files to pull targets from metadata
* refactor: Add shinyalerts package for pop up notifications
* docs: Update DESCRIPTION Imports

# CAST_Shiny 0.0.2.9003 (2025-10-08)

* refactor: Add placeholder for running skeleton code
* refactor: Disable and enable buttons
    + Report

# CAST_Shiny 0.0.2.9002 (2025-09-24)

* refactor: Change names of folder in app to match skeleton code

# CAST_Shiny 0.0.2.9001 (2025-09-04)

* refactor: Move Shiny apps from `CASTfxn` repo to this repo

# CAST_Shiny 0.0.1.9017 (2025-08-25)

* refactor: Add CASToolClusterPckg

# CAST_Shiny 0.0.1.9016 (2025-08-22)

* fix: Correct typo in zip command for wshed stressors GitHub download

# CAST_Shiny 0.0.1.9015 (2025-08-22)

* refactor: Change from zip::zip to utils::zip
    + zip::zip not working on ShinyApps.io

# CAST_Shiny 0.0.1.9014 (2025-08-22)

* refactor: Ensure data and result folders exist on start up

# CAST_Shiny 0.0.1.9013 (2025-08-21)

* refactor: Update select input of target sites based on checked files

# CAST_Shiny 0.0.1.9012 (2025-08-21)

* refactor: Rework how uploaded files are checked for inclusion in metadata

# CAST_Shiny 0.0.1.9011 (2025-08-19)

* refactor: Address comments 2025-08-18 on 2025-08-07 version of app

# CAST_Shiny 0.0.1.9010 (2025-08-19)

* feature: Update Shiny Apps prep routine
		+ Add blank file before upload to ShinyApps.io
		    - Upload does not transfer empty folders

# CAST_Shiny 0.0.1.9009 (2025-08-19)

* refactor: Address comments 2025-08-18 on 2025-08-07 version of app

# CAST_Shiny 0.0.1.9008 (2025-08-07)

* refactor: Change utils::unzip to zip::unzip for use on ShinyApps.io

# CAST_Shiny 0.0.1.9007 (2025-08-07)

* feat: Build out most of initial wireframe design

# CAST_Shiny 0.0.1.9006 (2025-07-29)

* refactor: Change case of text to be consistent for buttons and titles

# CAST_Shiny 0.0.1.9005 (2025-07-29)

* fix: Add shinyBS library to global

# CAST_Shiny 0.0.1.9004 (2025-07-29)

+ refactor: Create wireframe with placeholders from 2025-06-02 Storyboard

# CAST_Shiny 0.0.1.9003 (2025-06-03)
+ docs: Update README badges

# CAST_Shiny 0.0.1.9002 (2025-06-03)
+ docs: Added and updated documentation to support GitHub repo
    - DESCRIPTION
    - NEWS
    - README

# CAST_Shiny 0.0.1.9001 (2025-06-03)
+ Initialized repo on GitHub
